---
title: "Coevolution data visualisation"
author: "Dr. Sarath Dantu"
date: "2023-03-27"
output: html_document
---

#Load the source R script containing the functions for plotting

```{r}
#set path to DyNoPy folder
path_to_dynopy="DyNoPy"
#no need to edit this variable
path_to_R_script=paste(path_to_dynopy,"/R/DyNoPy_R_graphs.R",sep="")
#loading the script
source(path_to_R_script)
```

#Load the coevolution matrix file
Please note the functions below are also applicable to visualise J-matrix or Scaled Coevolution Score matrix or any data in matrix format.

```{r}
#this is the file generate from dyno_1_coevolution.py
file_co_matrix<-"path/to/the/file/filename.mat"
coevolution_matrix<-as.matrix(read.table(file_co_matrix,header=F))
```

This file "Residue_stats.txt" is generated from dyno_4_networks.py -o option. It contains the following data

*Residue ID
*Community ID: community number to which the residue belongs to based on cut-off score of modularity Q
*EVC: Eigenvector centrality score, tells you how imporant a residue is, 0: not imporant, 1: very important
*C_CS: Cummulative coevolution score calculated over all pairs for that residue $r_i$
*C_SCS: Cummulative scaled (by mean) coevolution score calculated over all pairs for that residue $r_i$
*C_J_Vec_x: Cummulative J score calculated over all pairs for that residue $r_i$, for the vector $x_i$

```{r}

file_residue_stats<-"path/to/the/file/filename.txt"

res_stats_df<-read.csv(file_residue_stats,header=T)
```

#Heat map to visualise the coevolution matrix
```{r}
dynor_mat_heatmap(coevolution_matrix,"Plot title")
```
#Boxplot to visualise the spread of coevolution scores by residue
```{r,fig.width=8}
dynor_mat_boxplot(coevolution_matrix,"Plot title")
```
#Line plot to visualise the coevolution scores by residue, with residues having mean coevolution scores greater than the mean shown in red

```{r}
dynor_mat_impplot(coevolution_matrix,"Plot title")
```

#Visualising Eigenvector centrality by Residue ID
```{r}
barplot(res_stats_df$EVC,ylab="Eigenvector centrality",xlab="Residue ID")
```

#Setting all EVC and community ID which are -1 to NA
```{r}
res_stats_df$EVC[res_stats_df$EVC<0]=NA
res_stats_df$CommunityID[res_stats_df$CommunityID<0]=NA
```

#Creating a table of memebership by community
```{r}
table_x<-table(res_stats_df$CommunityID)
```

#Visualising spread of EVC by community
```{r}
par(las=2)
bx<-boxplot(EVC~CommunityID,data=res_stats_df,xlab="# Community ID",ylab="Eigenvector Centrality",ylim=c(-0.25,1),yaxt='n')
text(x=as.integer(bx$names),y=-0.2,labels=as.vector(table_x),col="blue",cex=0.8)
axis(2,seq(0,1,0.1))
```
#Membership of communities
```{r}
barplot(table(res_stats_df$CommunityID),ylim=c(0,20))
```
